---
title: "Interpolation de donnees pour 1 capteur"
author : LEGRAND Louis, TU Philippe
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE,results='hide',message=FALSE}
library(plyr)
library(dplyr)
library(zoo)
```
## Importation des librairies & Préparation des données
```{r echo=FALSE,message=FALSE}
# Used to convert factor to proper numeric class variables
as.numeric.factor <- function(x) {as.numeric(levels(x))[x]}
# File names that will be imported
lux_sensor_0_filename<-"converted_volt_to_lux_AllDatas_20160329_205341_ch0_output.csv"
coordinates_0_filename<-"capteur0.csv"
# Column Names 
lux_sensor_column_names<-c("Timestamp_coordinates","Lux")
coordinates_sensorcol_names<-c("Timestamp_coordinates","X","Y")
# Opening files that will be needed 
sensor_0_dataset<-read.csv(lux_sensor_0_filename, header=FALSE, sep=",")
coordinates_sensor_0_data<-read.csv(file=coordinates_0_filename,header=FALSE,sep = ",")
#Drop first columns of coordinates_sensor files : 
coordinates_sensor_0_data$V1<-NULL
# Naming columns OK
colnames(sensor_0_dataset)<-lux_sensor_column_names
colnames(coordinates_sensor_0_data)<-coordinates_sensorcol_names
# Delete the first row of each file 
sensor_0_dataset<-data.frame(sensor_0_dataset[-1,])
coordinates_sensor_0_data<-data.frame(coordinates_sensor_0_data[-1,])
# Resetting row names 
rownames(sensor_0_dataset) <- seq(length=nrow(sensor_0_dataset)) 
rownames(coordinates_sensor_0_data) <- seq(length=nrow(coordinates_sensor_0_data)) 
# Taking out the first minute of timestamp in each coordinates_sensor files
minute_milliseconds=as.numeric(coordinates_sensor_0_data[1,1])+60000000
coordinates_sensor_0_data = subset(coordinates_sensor_0_data,as.numeric.factor(Timestamp_coordinates)>minute_milliseconds)
rownames(coordinates_sensor_0_data) <- seq(length=nrow(coordinates_sensor_0_data)) 
head(coordinates_sensor_0_data,10)
```


```{r echo=FALSE,message=FALSE,results='hide',message=FALSE}
#Creating vectors containing an offset row
temp0 <- c(0,as.numeric.factor(coordinates_sensor_0_data$Timestamp_coordinates))
ft_delta<-function(timestamp,timestamp_offset){
  res<-as.character(timestamp-timestamp_offset)
  return(res)
}
#Taking out the first row
temp0<-head(temp0,-1)
#Creating delta_TimeStamp column
coordinates_sensor_0_data$delta_TimeStamp<-mapply(ft_delta,as.numeric.factor(coordinates_sensor_0_data$Timestamp_coordinates),temp0)
#Shift row up of one row 
shift <- function(x, n){
  c(x[-(seq(n))], rep(NA, n))
}
#Shifting rows on GPS coordinates file
coordinates_sensor_0_data$delta_TimeStamp<-shift(coordinates_sensor_0_data$delta_TimeStamp,1)
head(coordinates_sensor_0_data,10)
```

##Données préparées,colonnes "X_offset","Y_offset","delta_TimeStamp" : colonnes X et Y décalées d'une ligne, difference de temps entre deux mesures GPS
```{r echo=FALSE,message=FALSE}
coordinates_sensor_0_data$Timestamp_gps <- coordinates_sensor_0_data$Timestamp_coordinates
coordinates_sensor_0_data$X_offset <- head(c(0, as.character(coordinates_sensor_0_data$X)), -1)
coordinates_sensor_0_data$Y_offset <- head(c(0, as.character(coordinates_sensor_0_data$Y)), -1)
head(coordinates_sensor_0_data,10)
```


```{r echo=FALSE,message=FALSE,results='hide',message=FALSE}
#Now Joining lux data frame with sensor dataframe
joined_dataframe_0<-full_join(coordinates_sensor_0_data,sensor_0_dataset)
# Sort timestamps
arranged_joined_dataframe_0<-arrange(joined_dataframe_0,as.numeric(Timestamp_coordinates))
# We take out 28 rows because we don't have the delta_TimeStamp for those 28 rows to do further calculations.
arranged_joined_dataframe_0<-slice(arranged_joined_dataframe_0,29:5772293)
head(arranged_joined_dataframe_0,10)
```
##On inclut les données des Luxmètres
##On duplique le contenu des colonnes récemment créées afin de faire correspondre des données GPS à chaque mesure de Luxmètre
```{r echo=FALSE,message=FALSE}
#Using na.locf to copy NA values by the most recent non-NA prior to it.
arranged_joined_dataframe_0$X<-na.locf(arranged_joined_dataframe_0$X)  
arranged_joined_dataframe_0$Y<-na.locf(arranged_joined_dataframe_0$Y)  
arranged_joined_dataframe_0$delta_TimeStamp<-na.locf(arranged_joined_dataframe_0$delta_TimeStamp)
arranged_joined_dataframe_0$Timestamp_gps<-na.locf(arranged_joined_dataframe_0$Timestamp_gps)
arranged_joined_dataframe_0$X_offset<-na.locf(arranged_joined_dataframe_0$X_offset)
arranged_joined_dataframe_0$Y_offset<-na.locf(arranged_joined_dataframe_0$Y_offset)
#Taking out all lines with NA
arranged_joined_dataframe_0<-na.omit(arranged_joined_dataframe_0)
head(arranged_joined_dataframe_0,10)
```
##On calcule les valeurs qui permettront le calcul des coordonnées finales (X,Y)
```{r echo=FALSE,message=FALSE}
#Calculate coordinates
#Difference between timestamp of lux measure and its lower GPS timestamp value
arranged_joined_dataframe_0$dif_lower_and_lux_timestamps<-as.numeric(arranged_joined_dataframe_0$Timestamp_coordinates)-as.numeric.factor(arranged_joined_dataframe_0$Timestamp_gps)
#Ratios
arranged_joined_dataframe_0$ratio_timestamps_lux<-(arranged_joined_dataframe_0$dif_lower_and_lux_timestamps*100)/as.numeric(arranged_joined_dataframe_0$Timestamp_gps)
#Absolute values
arranged_joined_dataframe_0$abs_x_diff<-abs(as.numeric.factor(arranged_joined_dataframe_0$X)-as.numeric(arranged_joined_dataframe_0$X_offset))
arranged_joined_dataframe_0$abs_y_diff<-abs(as.numeric.factor(arranged_joined_dataframe_0$Y)-as.numeric(arranged_joined_dataframe_0$Y_offset))
#Sign difference to know if we will have to substract or add when we will calculate final X and Y
arranged_joined_dataframe_0$sign_diff_x<-sign(as.numeric( arranged_joined_dataframe_0$X )-as.numeric(arranged_joined_dataframe_0$X_offset))
arranged_joined_dataframe_0$sign_diff_y<-sign(as.numeric( arranged_joined_dataframe_0$Y )-as.numeric(arranged_joined_dataframe_0$Y_offset))
head(arranged_joined_dataframe_0,10)
```

#Nous utilisons toutes les données précédentes pour calculer les coordonnées finales (X,Y) avec ifelse
```{r echo=FALSE,message=FALSE}
#If sign_diff_x ==1 : 
arranged_joined_dataframe_0$final_x<-ifelse(arranged_joined_dataframe_0$sign_diff_x==1,as.character(as.numeric(arranged_joined_dataframe_0$X_offset) + (arranged_joined_dataframe_0$abs_x_diff/100)*arranged_joined_dataframe_0$ratio_timestamps_lux),as.character(as.numeric(arranged_joined_dataframe_0$X_offset) - (arranged_joined_dataframe_0$abs_x_diff/100)*arranged_joined_dataframe_0$ratio_timestamps_lux))
arranged_joined_dataframe_0$final_y<-ifelse(arranged_joined_dataframe_0$sign_diff_y==1,as.character(as.numeric(arranged_joined_dataframe_0$Y_offset) + (arranged_joined_dataframe_0$abs_y_diff/100)*arranged_joined_dataframe_0$ratio_timestamps_lux),as.character(as.numeric(arranged_joined_dataframe_0$Y_offset) - (arranged_joined_dataframe_0$abs_y_diff/100)*arranged_joined_dataframe_0$ratio_timestamps_lux))
#Now we have all data to put it on a map,
final_result_sensor_0<-subset(arranged_joined_dataframe_0,select=c("Timestamp_coordinates","final_x","final_y","Lux"))
rownames(final_result_sensor_0) <- seq(length=nrow(final_result_sensor_0)) 
head(final_result_sensor_0,10)
```

write.csv(final_result_sensor_0,file="capteur_0",row.names=FALSE)
